Exploring Hillary Clinton's Emails\thanks{STATS 601 final project. All of the code used to download, process, and analyze the data for this project is available at \url{https://github.com/lbybee/601_Final_Project} and has been open-sourced under the MIT license.}

### 2016-04-20 paper/paper.tex
More editing.

\title{Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}}
\author{
    Leland Bybee, Roger Fan, Ryan Vaughn
}
\date{\today}

@@

\subsection{Interpreting Topics}

After choosing and estimating our topic model, the first task is to check whether we can actually find meaning in the resulting topics. If topics correspond to meaningful issues or structures then we can use these results to make useful observations about the data.

@@

Analysis is most easily done by examining the top words from each topics to find patterns and themes. Table~\ref{tab:top_words} shows the top 10 words for each of the 30 estimated topics. The LDA algorithm makes no attempt to interpret these meanings, but by viewing them there are several easily distinguishable patterns. For example, many of the top words in Topic~6 relate to Israel and Palestine. Not every topic is as well-identified as this, and some of the estimated topics are thematically weaker than others, but overall the topics seems to correspond very well to interpretable subjects.

@@

We can see that the model effectively identifies words human observers would associate with these events. Topic~11 picks up on both of the primary political parties in the United States as well as other words associated with elections, such as politics, percent, and candidate.  Similarly, the Topic~23 identifies words that associated with international development, including develop, support, and global.

@@

\subsection{Multinomial Logistic Regression}

While the above results do give some sense of which senders are most associated with which topics, we next want to formalize this approach and get more general results that can more easily show us which senders are most related to each topic.  To approach this problem we turn to multinomial logistic regression as a solution.  Multinomial logistic regression generalizes the logistic regression approach to the case with more labels than two.  Part of the output of multinomial logistic regression is a $P \times K$ matrix of coefficients corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.

@@

\section{Conclusion}

We have presented a series of results to attempt to make a large corpus of emails that would be difficult to parse manually approachable to the human user.  We have been able to identify general structures in the email corpus using both spectral clustering and LDA.  For LDA we find that we can seperate out content topics from structural topics and that the topics we get back are sensible and align with what we would expect in the real world.  Additionally, we find that we can say something interesting about the senders for our email corpus.

>>>>

\title{Exploring Hillary Clinton's Emails\thanks{STATS 601 final project. All of the code used to download, process, and analyze the data for this project is available at \url{https://github.com/lbybee/601_Final_Project} and has been open-sourced under the MIT license.}}
\author{
    Leland Bybee, Roger Fan, Ryan Vaughn
}
\date{April 22, 2016}

@@

\subsection{Interpreting Topics}
After choosing and estimating our topic model, the first task is to check whether we can actually find meaning in the resulting topics. If topics correspond to meaningful issues or structures then we can use these results to make useful observations about the data.

@@

Interpretation is most easily done by examining the top words from each topics to find patterns and themes. Table~\ref{tab:top_words} shows the top 10 words for each of the 30 estimated topics. The LDA algorithm makes no attempt to interpret these meanings, but by viewing them there are several easily distinguishable patterns. For example, many of the top words in Topic~6 relate to Israel and Palestine. Not every topic is as well-identified as this, and some of the estimated topics are thematically weaker than others, but overall the topics seems to correspond very well to interpretable subjects.

@@

The model seems to effectively identify words that human observers would associate with these events. Topic~11 picks up on both of the primary political parties in the United States as well as other words associated with elections, such as politics, percent, and candidate.  Similarly, the Topic~23 identifies words that associated with international development, including develop, support, and global.

@@

\subsection{Multinomial Logistic Regression}
While the above results do give some sense of which senders are most associated with which topics, we next want to formalize this approach and get more general results that can more easily show us which senders are most related to each topic.  To approach this problem we turn to multinomial logistic regression as a solution.  Multinomial logistic regression generalizes the logistic regression approach to the case with more labels than two.  Part of the output of multinomial logistic regression is a $P \times K$ matrix of coefficients corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.

@@

\section{Conclusion}
We have presented a series of results to attempt to make a large corpus of emails that would be difficult to parse manually approachable to the human user.  We have been able to identify general structures in the email corpus using both spectral clustering and LDA.  For LDA we find that we can seperate out content topics from structural topics and that the topics we get back are sensible and align with what we would expect in the real world.  Additionally, we find that we can say something interesting about the senders for our email corpus.
